Combined Task and Motion Planner through an Interface Layer

### 2015-04-18 documentation/draft.tex

The two immediately relevant open questions are whether it's possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.

-include more grasp primitives (e.g. push grasps)

-partially observable or non-deterministic environments

-replanning online

>>>>

The two immediately relevant open questions are whether it's possible to design a similar interface between task and motion plans which returns optimal plans or which can be used to do online planning.
Currently, the interface layer works only in deterministic, fully observable environments.  
It would be very interesting to develop similar algorithms to work in non-deterministic or partially observable environments as well.

Other interesting and relevant extensions could include the addition of more grasp primitives, for instance, push grasp primitives.
